Altering Backward Pass Gradients improves Convergence

### 2022-09-19 paper.tex
Mod8

\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{PGT_Types}
\caption{ Different ways of altering gradients in the backward pass. Blue blocks denote
a CNN's different layers (convolutional, linear, batchnorm, softmax, etc.). Orange
blocks indicate the backward graph with unmodified gradients. Green blocks represent
transformation functions, while red blocks indicate transformed gradients. (a)
\textbf{Type 0:} Backpropagation without any gradient modification. (b) \textbf{Type I:}
Altering gradients after they are all computed. (c) \textbf{Type II:} Altering gradients
at an earlier stage in the backward computation graph, subsequently leading to
alteration of all other gradients. }
\label{fig:gradient_altering}
\end{figure}

@@

\item We introduce PowerGrad Transform, which decouples the backward and the forward
passes of neural network training and enables a considerably better fit to the dataset,
as assessed by both training and test accuracy measures. PGT is a performance
enhancement method that alters the gradients in the backward pass before the update step
leading to significant boost in network's predictive performance.

@@

\begin{figure}[t]
\centering
\begin{subfigure}{.5\columnwidth}
\centering
\includegraphics[width=0.96\columnwidth]{prob_transform_unordered}
\caption{Unordered distribution}
\end{subfigure}%
\begin{subfigure}{.5\columnwidth}
\centering
\includegraphics[width=0.96\columnwidth]{prob_transform_ordered}
\caption{Rank ordered distribution}
\end{subfigure}
\caption{ Illustration of the impact of PowerGrad Transform on probability values of an
arbitrary distribution (number of classes, $C=10$). $\alpha=1$ indicates the unmodified
distribution. As $\alpha$ reduces from $1$ to $0$, the probability distributions (left:
unordered or right: ordered) becomes flatter and flatter, approaching the uniform
distribution of $1/C$ for every index. }
\label{fig:prob_plots}
\end{figure}

@@

\begin{figure}[!t]
\centering
\begin{subfigure}{.5\columnwidth}
\centering
\includegraphics[width=0.9\columnwidth]{acc_vs_epoch_r18}
\caption{Plot of training and test accuracies (ResNet-18)}
\end{subfigure}%
\begin{subfigure}{.5\columnwidth}
\centering
\includegraphics[width=0.9\columnwidth]{acc_vs_epoch_r50}
\caption{Plot of training and test accuracies (ResNet-50)}
\end{subfigure}
\caption{ Log-linear plots of training and test accuracies and comparison with baseline
of batch-normalized variants: \textbf{(a)} ResNet-18 ($\alpha=0.25$), \textbf{(b)}
ResNet-50 ($\alpha=0.3$). For better visualization of accuracies obtained in the final
iterations, we plot both axes in log scale. PowerGrad Transform improves upon the
baseline in all cases. The corresponding accuracies are mentioned in table
\ref{tab:imagenet_table}. }
\label{fig:metrics}
\end{figure}

@@

In our experiments with Squeeze-and-Excitation variant of ResNet-50 i.e.
SE-ResNet-50\cite{hu2018squeeze}, we observe significant improvements; a $0.97\%$ boost
in training accuracy and a $0.734\%$ increase in test accuracy. These improvements are
obtained with the number of epochs being kept the same as that of the baseline model.
Alternatively, practioners can choose to employ PGT and have the networks converge to
accuracies similar to that of the baseline with a much lower epoch budget. We explore
this in detail in section \ref{sec:speed}. Therefore, PGT also speeds up training. In
our experiments with ResNet-50, we find an increase of $0.5\%$ and $0.656\%$ performance
enhancement over the baseline while using the cosine scheduler. The corresponding
improvement over the step scheduler baseline for ResNet-50 is $0.57\%$ and $0.524\%$
respectively for training and testing. ResNet-101 sees a higher improvement in training
fit, $0.81\%$ to be exact, while the improvement over the test set is $0.362\%$. Smaller
networks such as SE-ResNet-18 and ResNet-18 sees accuracy boosts which are smaller but
nevertheless positive. Therefore we conclude that with PGT, the consistent improvements
in training accuracies across all cases is because the networks train better and arrive
at better optimas during convergence. Per epoch training and test accuracy plots of
ResNet-18 and ResNet-50 (both with and without PGT) are shown in Fig.
\ref{fig:metrics}(a, b). For better visualization of the top end of the plots, we scale
both axes in log scale. Our experiments with batch-normalized networks indicate that
PowerGrad Transform speeds up training and allows the network to learn better
representations\footnote{Reproducible code, training recipes for the experiments,
pretrained checkpoints and training logs are provided at: \\
\url{ https://github.com/bishshoy/power-grad-transform }. Code is adapted from
\cite{rw2019timm}.}.

@@

\begin{subfigure}[t]{0.32\textwidth}
\includegraphics[width=\linewidth]{baseline-w-layer-4-2}
\caption{Norm of filters of convolutional layer 11 (without PGT)}
\end{subfigure}
\begin{subfigure}[t]{0.32\textwidth}
\includegraphics[width=\linewidth]{baseline-w-layer-7-2}
\caption{Norm of filters of the final convolutional layer (without PGT)}
\end{subfigure}
\begin{subfigure}[t]{0.32\textwidth}
\includegraphics[width=\linewidth]{baseline-f-layer-22-1}
\caption{Norm of final layer's output features (without PGT)}
\end{subfigure}

\begin{subfigure}[t]{0.32\textwidth}
\includegraphics[width=\linewidth]{pgt-w-layer-4-2}
\caption{Norm of filters of convolutional layer 11 (with PGT)}
\end{subfigure}
\begin{subfigure}[t]{0.32\textwidth}
\includegraphics[width=\linewidth]{pgt-w-layer-7-2}
\caption{Norm of filters of the final convolutional layer (with PGT)}
\end{subfigure}
\begin{subfigure}[t]{0.32\textwidth}
\includegraphics[width=\linewidth]{pgt-f-layer-22-1}
\caption{Norm of final layer's output features (with PGT)}
\end{subfigure}
\captionsetup{font=normalsize}
\caption{ Experiment demonstrating the Zeroing Out phenomena, as observed in different
filters and feature vectors. PGT greatly reduces the zeroing out of filters and promote
better learning. }
\label{fig:norm_plots}
\end{figure}

@@

\begin{subfigure}[t]{0.32\textwidth}
\includegraphics[width=\linewidth]{baseline-w-layer-5-3}
\caption{Norm of filters of layer 15 (without AGC/PGT)}
\end{subfigure}
\begin{subfigure}[t]{0.32\textwidth}
\includegraphics[width=\linewidth]{pgt-w-layer-5-3}
\caption{Norm of filters of layer 15 (with PGT)}
\end{subfigure}
\begin{subfigure}[t]{0.32\textwidth}
\includegraphics[width=\linewidth]{agc_pgt-w-layer-5-3}
\caption{Norm of filters of layer 15 (with AGC+PGT)}
\end{subfigure}

\begin{subfigure}[t]{0.32\textwidth}
\includegraphics[width=\linewidth]{baseline-w-layer-1-2}
\caption{Norm of filters of layer 2 (without AGC/PGT)}
\end{subfigure}
\begin{subfigure}[t]{0.32\textwidth}
\includegraphics[width=\linewidth]{pgt-w-layer-1-2}
\caption{Norm of filters of layer 2 (with PGT)}
\end{subfigure}
\begin{subfigure}[t]{0.32\textwidth}
\includegraphics[width=\linewidth]{agc_pgt-w-layer-1-2}
\caption{Norm of filters of layer 2 (with AGC+PGT)}
\end{subfigure}
\captionsetup{font=normalsize}
\caption{ Experiment demonstrating the efficacy of PGT and AGC+PGT, as observed in
different layers. }
\label{fig:agc_pgt}
\end{figure}

@@

\begin{figure}[t]
\centering
\begin{subfigure}{.33\columnwidth}
\centering
\includegraphics[width=0.96\columnwidth]{logit_vs_alpha}
\caption{\\Logit vs. $\alpha$}
\end{subfigure}%
\begin{subfigure}{.33\columnwidth}
\centering
\includegraphics[width=0.96\columnwidth]{loss_vs_alpha}
\caption{\\Cross-entropy loss vs. $\alpha$}
\end{subfigure}%
\begin{subfigure}{.33\columnwidth}
\centering
\includegraphics[width=0.96\columnwidth]{logit_vs_loss}
\caption{\\Logit-Loss correlation}
\end{subfigure}
\caption{ Plots of various statistical measures: \textbf{(a)} Variations in the logit
norm vs. $\alpha$. The logit norm is calculated per image over the test set of
ImageNet-1K (at the linear layer of the ResNet-18 architecture) and then averaged.
\textbf{(b)} Variations in the final loss values obtained for different $\alpha$
settings. \textbf{(c)} Correlation between loss and logits. Regression line equation
:$(0.01074 x + 0.25816)$. }
\label{fig:stats}
\end{figure}

@@

We introduced PowerGrad Transform, which decouples the backward and forward passes of
neural network training and enables a significantly better fit to the dataset, as
measured by training and test accuracy metrics. We show the application of PowerGrad
Transform, a simple yet powerful technique for modifying the gradient flow behaviour. We
investigate experimentally the degenerate behavior of non-BN networks, which is
frequently observed during the standard training approach, especially with higher batch
sizes. With PGT, gradient behavior is enhanced and the likelihood of weights attaining
degenerate states is diminished. We provide a theoretical analysis of the PowerGrad
transformation. With the use of different network topologies and datasets, we are able
to show the potential of PGT and explore its impacts from an empirical standpoint. We
provide comprehensive results on a number of models (non-BN and BN ResNets, SE-ResNets)
using the ImageNet dataset. PGT helps the network to improve its learning capabilities
by locating a more optimum convergence point. In addition, we undertake an ablation
research and compare its effects to those of regularization methods such label
smoothing.

@@

\begin{figure}[h] \hrule \lstinputlisting[language=Python]{code.py} \hrule
\vspace{0.1cm} \caption{Python code of PowerGrad Transform based on PyTorch. }
\label{fig:code}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.5\columnwidth]{r18_grid_search}
\caption{ Grid search for various values of $\alpha$ for ResNet-18 architecture with the
ImageNet dataset. Each datapoint is collected over a 50 epoch budget, with other
hyperparameters kept the same as mentioned in section \ref{sec:bn}. }
\label{fig:grid_searcha}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=0.5\columnwidth]{r50_grid_search}
\caption{ Grid search for various values of $\alpha$ for ResNet-50 architecture with the
ImageNet dataset. Each datapoint is collected over a 50 epoch budget, with other
hyperparameters kept the same as mentioned in section \ref{sec:bn}. }
\label{fig:grid_searchb}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=0.5\columnwidth]{cifar10_grid_search}
\caption{\\ResNet-20 CIFAR-10}
\caption{ Grid search for various values of $\alpha$ for ResNet-20 architecture with the
CIFAR-10 dataset. Each datapoint is collected over a 360 epoch budget. }
\label{fig:grid_searchc}
\end{figure}

@@

\subsection{Norm plots of weights (baseline (low batch size)) of non-BN
ResNet-18}
\begin{figure}[h] \centering \includegraphics[width=0.55\textwidth]{baseline-w_norm}
\caption{ Method: baseline, batch size = 256. This is a plot depicting the
iteration-wise evolution of the norm of each filter in each layer. Each subplot
corresponds to a layer of the unnormalized ResNet-18. Above each subplot, the layer
indices are shown. Each filter in each subplot is shown with a separate and randomly
determined colour. } \end{figure}

@@

\subsection{Norm plots of weights (baseline (high batch size)) of non-BN
ResNet-18}
\begin{figure}[h] \centering
\includegraphics[width=0.55\textwidth]{baseline_high_bs-w_norm} \caption{ Method:
baseline (high batch size), batch size = 1024. This is a plot depicting the
iteration-wise evolution of the norm of each filter in each layer. Each subplot
corresponds to a layer of the unnormalized ResNet-18. Above each subplot, the layer
indices are shown. Each filter in each subplot is shown with a separate and randomly
determined colour. } \end{figure}

@@

\subsection{Norm plots of weights (PGT) of non-BN ResNet-18}
\begin{figure}[h] \centering \includegraphics[width=0.55\textwidth]{pgt-w_norm}
\caption{ Method: PGT, batch size = 256. This is a plot depicting the iteration-wise
evolution of the norm of each filter in each layer. Each subplot corresponds to a layer
of the unnormalized ResNet-18. Above each subplot, the layer indices are shown. Each
filter in each subplot is shown with a separate and randomly determined colour. }
\end{figure}

@@

\subsection{Norm plots of weights (AGC + PGT) of non-BN ResNet-18}
\begin{figure}[h] \centering \includegraphics[width=0.55\textwidth]{agc_pgt-w_norm}
\caption{ Method: AGC + PGT, batch size = 256. This is a plot depicting the
iteration-wise evolution of the norm of each filter in each layer. Each subplot
corresponds to a layer of the unnormalized ResNet-18. Above each subplot, the layer
indices are shown. Each filter in each subplot is shown with a separate and randomly
determined colour. } \end{figure}

@@

\begin{figure}[h] \centering \includegraphics[width=0.96\columnwidth]{drawing} \caption{
ResNet-18 architecture with layer indices of convolutional layers and the number of
filters in each layer. } \label{fig:resnet18} \end{figure}

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=\textwidth]{PGT_Types}
\caption{ Different ways of altering gradients in the backward pass. Blue blocks denote
a CNN's different layers (convolutional, linear, batchnorm, softmax, etc.). Orange
blocks indicate the backward graph with unmodified gradients. Green blocks represent
transformation functions, while red blocks indicate transformed gradients. (a)
\textbf{Type 0:} Backpropagation without any gradient modification. (b) \textbf{Type I:}
Altering gradients after they are all computed. (c) \textbf{Type II:} Altering gradients
at an earlier stage in the backward computation graph, subsequently leading to
alteration of all other gradients. }
\label{fig:gradient_altering}
\end{figure}

@@

\item We introduce PowerGrad Transform, which decouples the backward and the forward
passes of neural network training and enables a considerably better fit to the dataset,
as assessed by both training and test accuracy measures. PGT is a performance
enhancement method that alters the gradients in the backward pass before the update step
leading to accelerated training and a significant boost in the network's predictive
performance.

@@

\begin{figure}[t]
\centering
\begin{subfigure}{.5\textwidth}
\centering
\includegraphics[width=0.98\textwidth]{prob_transform_unordered}
\caption{Unordered distribution}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
\centering
\includegraphics[width=0.98\textwidth]{prob_transform_ordered}
\caption{Rank ordered distribution}
\end{subfigure}
\caption{ Illustration of the impact of PowerGrad Transform on probability values of an
arbitrary distribution (number of classes, $C=10$). $\alpha=1$ indicates the unmodified
distribution. As $\alpha$ reduces from $1$ to $0$, the probability distributions (left:
unordered or right: ordered) becomes flatter and flatter, approaching the uniform
distribution of $1/C$ for every index. }
\label{fig:prob_plots}
\end{figure}

@@

\begin{figure}[!t]
\centering
\begin{subfigure}{.33\textwidth}
\centering
\includegraphics[width=0.98\textwidth]{acc_vs_epoch_r18}
\caption{Plot of training and test accuracies (ResNet-18)}
\end{subfigure}%
\begin{subfigure}{.33\textwidth}
\centering
\includegraphics[width=0.98\textwidth]{acc_vs_epoch_r50}
\caption{Plot of training and test accuracies (ResNet-50)}
\end{subfigure}%
\begin{subfigure}{.33\textwidth}
\centering
\includegraphics[width=0.98\textwidth]{acc_vs_epoch_r50_60epochs}
\caption{Plot of test accuracies (ResNet-50)}
\end{subfigure}
\caption{ Log-linear plots of training and test accuracies and comparison with baseline
of batch-normalized variants: \textbf{(a)} ResNet-18 ($\alpha=0.25$), \textbf{(b)}
ResNet-50 ($\alpha=0.3$). For better visualization of accuracies obtained in the final
iterations, we plot both axes in log scale. PowerGrad Transform improves upon the
baseline in all cases. The corresponding accuracies are mentioned in table
\ref{tab:imagenet_table}. \textbf{(c)} Training speed comparison between PGT ($60$
epochs) and baseline ($100$ epochs). They both converge to the same test accuracy
($76.5\%$) on ImageNet-1K. PGT's accelerated training saves $40\%$ of the epoch budget.
}
\label{fig:metrics}
\end{figure}

@@

In our experiments with Squeeze-and-Excitation variant of ResNet-50 i.e.
SE-ResNet-50\cite{hu2018squeeze}, we observe significant improvements; a $0.97\%$ boost
in training accuracy and a $0.734\%$ increase in test accuracy. Therefore, PGT also
speeds up training. In our experiments with ResNet-50, we find an increase of $0.5\%$
and $0.656\%$ performance enhancement over the baseline while using the cosine
scheduler. The corresponding improvement over the step scheduler baseline for ResNet-50
is $0.57\%$ and $0.524\%$ respectively for training and testing. ResNet-101 sees a
higher improvement in training fit, $0.81\%$ to be exact, while the improvement over the
test set is $0.362\%$. Smaller networks such as SE-ResNet-18 and ResNet-18 sees accuracy
boosts which are smaller but nevertheless positive. Therefore we conclude that with PGT,
the consistent improvements in training accuracies across all cases is because the
networks train better and arrive at better optimas during convergence. Per epoch
training and test accuracy plots of ResNet-18 and ResNet-50 (both with and without PGT)
are shown in Fig. \ref{fig:metrics}(a, b). For better visualization of the top end of
the plots, we scale both axes in log scale. Our experiments with batch-normalized
networks indicate that PowerGrad Transform speeds up training and allows the network to
learn better representations\footnote{Reproducible code, training recipes for the
experiments, pretrained checkpoints and training logs are provided at: \\
\url{ https://github.com/bishshoy/power-grad-transform }. Code is adapted from
\cite{rw2019timm}.}.

These improvements are obtained with the number of epochs being kept the same as that of
the baseline model. Alternatively, practitioners can apply PGT and have the networks
converge to accuracy levels comparable to the baseline with a significantly reduced
epoch budget. In Fig. \ref{fig:metrics}(c), we illustrate one such instance in which we
train a ResNet-50 to its cosine scheduler baseline in just $60$ epochs with PGT, and
match its baseline performance that is acquired in $100$ epochs. Because of the
acceleration in training that is made possible by PGT, the total amount of training time
can be decreased by $40\%$.

@@

\begin{subfigure}[t]{0.33\textwidth}
\includegraphics[width=\textwidth]{baseline-w-layer-4-2}
\caption{Norm of filters of convolutional layer 11 (without PGT)}
\end{subfigure}
\begin{subfigure}[t]{0.33\textwidth}
\includegraphics[width=\textwidth]{baseline-w-layer-7-2}
\caption{Norm of filters of the final convolutional layer (without PGT)}
\end{subfigure}
\begin{subfigure}[t]{0.33\textwidth}
\includegraphics[width=\textwidth]{baseline-f-layer-22-1}
\caption{Norm of final layer's output features (without PGT)}
\end{subfigure}

\begin{subfigure}[t]{0.33\textwidth}
\includegraphics[width=\textwidth]{pgt-w-layer-4-2}
\caption{Norm of filters of convolutional layer 11 (with PGT)}
\end{subfigure}
\begin{subfigure}[t]{0.33\textwidth}
\includegraphics[width=\textwidth]{pgt-w-layer-7-2}
\caption{Norm of filters of the final convolutional layer (with PGT)}
\end{subfigure}
\begin{subfigure}[t]{0.33\textwidth}
\includegraphics[width=\textwidth]{pgt-f-layer-22-1}
\caption{Norm of final layer's output features (with PGT)}
\end{subfigure}
\captionsetup{font=normalsize}
\caption{ Experiment demonstrating the Zeroing Out phenomena, as observed in different
filters and feature vectors. PGT greatly reduces the zeroing out of filters and promote
better learning. }
\label{fig:norm_plots}
\end{figure}

@@

\begin{subfigure}[t]{0.33\textwidth}
\includegraphics[width=\textwidth]{baseline-w-layer-5-3}
\caption{Norm of filters of layer 15 (without AGC/PGT)}
\end{subfigure}
\begin{subfigure}[t]{0.33\textwidth}
\includegraphics[width=\textwidth]{pgt-w-layer-5-3}
\caption{Norm of filters of layer 15 (with PGT)}
\end{subfigure}
\begin{subfigure}[t]{0.33\textwidth}
\includegraphics[width=\textwidth]{agc_pgt-w-layer-5-3}
\caption{Norm of filters of layer 15 (with AGC+PGT)}
\end{subfigure}

\begin{subfigure}[t]{0.33\textwidth}
\includegraphics[width=\textwidth]{baseline-w-layer-1-2}
\caption{Norm of filters of layer 2 (without AGC/PGT)}
\end{subfigure}
\begin{subfigure}[t]{0.33\textwidth}
\includegraphics[width=\textwidth]{pgt-w-layer-1-2}
\caption{Norm of filters of layer 2 (with PGT)}
\end{subfigure}
\begin{subfigure}[t]{0.33\textwidth}
\includegraphics[width=\textwidth]{agc_pgt-w-layer-1-2}
\caption{Norm of filters of layer 2 (with AGC+PGT)}
\end{subfigure}
\captionsetup{font=normalsize}
\caption{ Experiment demonstrating the efficacy of PGT and AGC+PGT, as observed in
different layers. }
\label{fig:agc_pgt}
\end{figure}

@@

\begin{figure}[t]
\centering
\begin{subfigure}{0.33\textwidth}
\centering
\includegraphics[width=0.98\textwidth]{logit_vs_alpha}
\caption{\\Logit vs. $\alpha$}
\end{subfigure}%
\begin{subfigure}{0.33\textwidth}
\centering
\includegraphics[width=0.98\textwidth]{loss_vs_alpha}
\caption{\\Cross-entropy loss vs. $\alpha$}
\end{subfigure}%
\begin{subfigure}{0.33\textwidth}
\centering
\includegraphics[width=0.98\textwidth]{logit_vs_loss}
\caption{\\Logit-Loss correlation}
\end{subfigure}
\caption{ Plots of various statistical measures: \textbf{(a)} Variations in the logit
norm vs. $\alpha$. The logit norm is calculated per image over the test set of
ImageNet-1K (at the linear layer of the ResNet-18 architecture) and then averaged.
\textbf{(b)} Variations in the final loss values obtained for different $\alpha$
settings. \textbf{(c)} Correlation between loss and logits. Regression line equation
:$(0.01074 x + 0.25816)$. }
\label{fig:stats}
\end{figure}

@@

We introduced PowerGrad Transform, which decouples the backward and forward passes of
neural network training and enables a significantly better fit to the dataset, as
measured by training and test accuracy metrics. We show the application of PowerGrad
Transform, a simple yet powerful technique for modifying the gradient flow behaviour. We
investigate experimentally the degenerate behavior of non-BN networks, which is
frequently observed during the standard training approach, especially with higher batch
sizes. With PGT, gradient behavior is enhanced and the likelihood of weights attaining
degenerate states is diminished. We provide a theoretical analysis of the PowerGrad
transformation. With the use of different network topologies and datasets, we are able
to show the potential of PGT and explore its impacts from an empirical standpoint. We
provide comprehensive results on a number of models (non-BN and BN ResNets, SE-ResNets)
using the ImageNet dataset. PGT helps the network to improve its learning capabilities
by locating a more optimum convergence point and simultaneously speeds up training. In
addition, we undertake an ablation research and compare its effects to those of
regularization methods such label smoothing.

@@

\begin{figure}[ht] \hrule \lstinputlisting[language=Python]{code.py} \hrule
\vspace{0.1cm} \caption{Python code of PowerGrad Transform based on PyTorch. }
\label{fig:code}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\columnwidth]{r18_grid_search}
\caption{ Grid search for various values of $\alpha$ for ResNet-18 architecture with the
ImageNet dataset. Each datapoint is collected over a 50 epoch budget, with other
hyperparameters kept the same as mentioned in section \ref{sec:bn}. }
\label{fig:grid_searcha}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\columnwidth]{r50_grid_search}
\caption{ Grid search for various values of $\alpha$ for ResNet-50 architecture with the
ImageNet dataset. Each datapoint is collected over a 50 epoch budget, with other
hyperparameters kept the same as mentioned in section \ref{sec:bn}. }
\label{fig:grid_searchb}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\columnwidth]{cifar10_grid_search}
\caption{\\ResNet-20 CIFAR-10}
\caption{ Grid search for various values of $\alpha$ for ResNet-20 architecture with the
CIFAR-10 dataset. Each datapoint is collected over a 360 epoch budget. }
\label{fig:grid_searchc}
\end{figure}

@@

\subsection{Norm plots of weights (baseline (low batch size)) of non-BN
ResNet-18}
\begin{figure}[ht] \centering \includegraphics[width=0.55\textwidth]{baseline-w_norm}
\caption{ Method: baseline, batch size = 256. This is a plot depicting the
iteration-wise evolution of the norm of each filter in each layer. Each subplot
corresponds to a layer of the unnormalized ResNet-18. Above each subplot, the layer
indices are shown. Each filter in each subplot is shown with a separate and randomly
determined colour. } \end{figure}

@@

\subsection{Norm plots of weights (baseline (high batch size)) of non-BN
ResNet-18}
\begin{figure}[ht] \centering
\includegraphics[width=0.55\textwidth]{baseline_high_bs-w_norm} \caption{ Method:
baseline (high batch size), batch size = 1024. This is a plot depicting the
iteration-wise evolution of the norm of each filter in each layer. Each subplot
corresponds to a layer of the unnormalized ResNet-18. Above each subplot, the layer
indices are shown. Each filter in each subplot is shown with a separate and randomly
determined colour. } \end{figure}

@@

\subsection{Norm plots of weights (PGT) of non-BN ResNet-18}
\begin{figure}[ht] \centering \includegraphics[width=0.55\textwidth]{pgt-w_norm}
\caption{ Method: PGT, batch size = 256. This is a plot depicting the iteration-wise
evolution of the norm of each filter in each layer. Each subplot corresponds to a layer
of the unnormalized ResNet-18. Above each subplot, the layer indices are shown. Each
filter in each subplot is shown with a separate and randomly determined colour. }
\end{figure}

@@

\subsection{Norm plots of weights (AGC + PGT) of non-BN ResNet-18}
\begin{figure}[ht] \centering \includegraphics[width=0.55\textwidth]{agc_pgt-w_norm}
\caption{ Method: AGC + PGT, batch size = 256. This is a plot depicting the
iteration-wise evolution of the norm of each filter in each layer. Each subplot
corresponds to a layer of the unnormalized ResNet-18. Above each subplot, the layer
indices are shown. Each filter in each subplot is shown with a separate and randomly
determined colour. } \end{figure}

@@

\begin{figure}[ht] \centering \includegraphics[width=0.96\columnwidth]{drawing} \caption{
ResNet-18 architecture with layer indices of convolutional layers and the number of
filters in each layer. } \label{fig:resnet18} \end{figure}
